---
title: "Install CmdStan"
output: pdf_document
---
## Installing the R package 

Run the following chunks if you don't have CmdStanR and/or CmdStan installed.

You can install the latest beta release of the CmdStanR R package with
```{r, eval = FALSE}
# Recommended running this in a fresh R session or restarting your current session
install.packages("cmdstanr", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
```

## Installing CmdStan

To instead install the latest development version of the package from GitHub use
```{r, eval = FALSE}
#Run this if you need to:
#install.packages("remotes")
remotes::install_github("stan-dev/cmdstanr")
```
If you don't already have CmdStan installed, then, in addition to installing

the R package, it is also necessary to install CmdStanR's
```{r, eval = FALSE}
install_cmdstan()
```
A suitable C++ toolchain is also required.

For more intructions and troubleshooting issues visit

https://mc-stan.org/cmdstanr/

https://mc-stan.org/cmdstanr/articles/cmdstanr.html

